Improving Cell Segmentation and Tracking via Mechanistic Models of Rod-Shaped Bacteria

### 2025-09-15 paper_segmentation_tracking/main.tex
add more todos
add preliminary figure of "fake-data reults"

%###################################################################################################
\section{(10\%) Methods}
% --------------------------------------------------------------------------------------------------
\subsection{Data Acquisition}
\begin{itemize}
    \item Use datasets from celltracking challenge
    \item possibly restrict to rod-shaped bacteria for now
\end{itemize}
% --------------------------------------------------------------------------------------------------
\subsection{Testing Methodology}
\begin{enumerate}
    \item Test model on Dataset
    \item Train model on additional data (possibly various configurations)
    \item Test again for same Dataset
\end{enumerate}

@@

>>>>

%###################################################################################################
\section{(10\%) Methods}
% --------------------------------------------------------------------------------------------------
\subsection{Data Acquisition}
\begin{itemize}
    \item Use datasets from celltracking challenge
    \item possibly restrict to rod-shaped bacteria for now
    \item maybe use remaining data to check that there is no overall regression within other samples
\end{itemize}
% --------------------------------------------------------------------------------------------------
\subsection{Testing Methodology}
\begin{enumerate}
    \item Test model on Dataset
    \item Train model on generated data (possibly various configurations)
    \item Test again for same Dataset
    \item Compare results
    \item Put in nice graphs
\end{enumerate}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{fake-figures/segmentation-benchmark.pdf}%
    \includegraphics[width=0.5\textwidth]{fake-figures/tracking-defects.pdf}
    \caption{
        Performance of various segmentation and tracking techniques.
        We will need various of such plots.
    }
\end{figure}
